---
title: "SEO Jobs Analysis"
author: "Cédric Scherer & Daniel Kupka (FrontPage Data) & Brian Dean (backlinko.com)"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: console
---

<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.showtext = TRUE)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})
```

```{r prep}
## packages
library(tidyverse)
library(tidytext)
library(pdftools)
library(showtext)

## save plots?
save <- TRUE
#save <- FALSE

## quality of png's
dpi <- 750

## font
font_add_google("Montserrat", "Montserrat")
font_add_google("Overpass Mono", "Overpass Mono")

## theme updates
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "Montserrat"))

theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(family = "Montserrat SemiBold",
                                       size = 16,
                                       face = "bold",
                                       lineheight = 1.15,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             #plot.title.position = "plot",
             plot.caption = element_text(color = "grey40", 
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(family = "Montserrat SemiBold",
                                         size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(family = "Montserrat SemiBold",
                                         size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))

## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)

## main color backlinko
bl_col <- "#00d188"

## colors + labels for interval stripes
int_cols <- c("#bce2d5", "#79d8b6", bl_col, "#009f66", "#006c45", "#003925")
int_perc <- c("100%", "95%", "75%", "50%", "25%", "5%")

## gradient colors for position
colfunc <- colorRampPalette(c(bl_col, "#bce2d5"))
pos_cols <- colfunc(10)
```

```{r data}
df <- readr::read_csv(here::here("raw_data", "Glassdoor - 2020-04-01-0.csv")) %>% 
  janitor::clean_names() %>% 
  dplyr::select(-url)
```


# 1. Job Title

## 1.1 Most Popular SEO Jobs

We analysed the data on job titles using text mining techniques. In a first step, we tokenize the job titles into single words and visualize their frequency. Stop words and words that appeared less than 7 times were removed to make the graph easier to grasp.

```{r 1-1-popular-job-words, fig.width = 12, fig.height = 9}
df %>% 
  unnest_tokens(word, job_title, token = "words") %>% 
  anti_join(stop_words) %>% 
  count(word, sort = T) %>% 
  filter(
    n > 7,
    word != "seo"
  ) %>% 
  mutate(word = if_else(word %in% c("sr", "ppc"), 
                        str_to_upper(word), 
                        str_to_title(word))) %>% 
  ggplot(aes(fct_reorder(word, n), n)) +
    geom_col(fill = bl_col, width = .8) +
    geom_text(aes(label = n),
              family = "Overpass Mono",
              color = "white",
              face = "bold",
              hjust = 1,
              nudge_y = -1) +
    coord_flip() +
    scale_y_continuous(expand = c(.01, .01)) +
    labs(x = NULL, 
         y = "Term frequence in job titles",
         caption = 'Note: Only words with a frequency of 8 or more shown. The term "SEO" was removed.') +
    theme_flip

if(save == T){
  ggsave(here::here("plots", "1_1_jobs_word.pdf"), width = 12, height = 9, device = cairo_pdf)
}
```


In a second step, we analysed sequences of words in the job title. The sorted bar plot shows the most popular consecutive sequences of words (5 or more occurences), colored by category.

```{r 1-1-popular-jobs-ngrams-cat, fig.width = 12, fig.height = 7.5}
df_job_ngrams <-
  df %>% 
  unnest_tokens(word, job_title, token = "ngrams") %>% 
  anti_join(stop_words) %>% 
  count(word, sort = T) %>% 
  filter(
    n > 4,
    !is.na(word)
  ) %>% 
  mutate(
    group = case_when(
      str_detect(word, "content") ~ "Content",
      str_detect(word, "manager") ~ "Management",
      str_detect(word, "analyst") ~ "Analysis",
      str_detect(word, "strategist") ~ "Strategy",
      str_detect(word, "optimiz") ~ "Optimization",
      str_detect(word, "market") ~ "Marketing",
      str_detect(word, "specialist") ~ "Analysis",
      TRUE ~ "Other"
    ),
    word = str_to_title(word)
  ) 
  
ggplot(df_job_ngrams, 
       aes(fct_reorder(word, n), n)) +
    geom_col(aes(fill = group), 
             width = .8) +
    geom_text(aes(label = n),
              family = "Overpass Mono",
              color = "white",
              face = "bold",
              hjust = 1,
              nudge_y = -.7) +
    coord_flip() +
    scale_y_continuous(expand = c(.01, .01)) +
    scale_fill_manual(name = "Job Category",
                      values = c("#2d6db4", "#633b96", "#e49e2e", "#b8318c", "#00b877", "#96633b")) +
    guides(fill = guide_legend(ncol = 1)) +
    labs(x = NULL, 
         y = "Frequence of word sequence in job titles",
         caption = "Note: Only sequences with a frequency of 5 or more shown.") +
    theme_flip +
    theme(legend.position = c(.68, .627),
          legend.key.size = unit(3, "pt"),
          legend.key.width = unit(30, "pt"))

if(save == T){
  ggsave(here::here("plots", "1_1_jobs_cat.pdf"), width = 12, height = 7.5, device = cairo_pdf)
}
```


We  manually classified in technical and non-technical positions, removing all words that are no specific to any of the both categories. This modified stacked bar plot shows the number of words found per job category and, additionally as another stacked bar next to it, the most common words per category (with labels for words that occured at least 20 times). The height of the stacks indicates as well the number, the width is arbitrary.

```{r 1-1-popular-job-type, fig.width = 12, fig.height = 12}
## technical: analyst, specialist, engineer, developer, technician, optimization,
## non-technical: manager, director, writer, consultant, coordinator, editor, marketing, sales, social media 

df_polar <-
  df %>% 
  unnest_tokens(word, job_title, token = "words") %>% 
  anti_join(stop_words) %>% 
  count(word, sort = T) %>% 
  mutate(
    type = case_when(
      str_detect(word, "analy|special|engine|develop|technic|optimi") ~ "technical",
      str_detect(word, "manage|direct|writ|consult|coordinat|edito|market|sale|social|strateg|supervis") ~ "non-technical",
      TRUE ~ "unknown"
    )
  ) %>%
  filter(type != "unknown") %>% 
  group_by(type) %>% 
  mutate(sum = sum(n)) %>% 
  ungroup %>% 
  arrange(sum, n) %>% 
  mutate(
    pos = cumsum(n),
    pos = if_else(!is.na(lag(pos)), pos - ((pos - lag(pos)) / 2), pos / 2)
  ) %>% 
  mutate(type = fct_reorder(factor(type), -sum)) %>% 
  mutate(country = fct_reorder2(factor(word), as.numeric(type), n, .desc = F)) %>% 
  group_by(type) %>%
  arrange(n) %>% 
  mutate(
    alpha = n / max(n),
    pos_cont = min(pos) + (max(pos) - min(pos)) / 2
  ) 

df_polar %>% 
  ggplot(aes(1, n)) +
    geom_col(
      aes(
        fill = type,
        fill = after_scale(colorspace::darken(fill, .05)), 
        color = type,
        color = after_scale(colorspace::darken(color, .15)), 
        alpha = alpha
      ), 
      size = .1
    ) +
    geom_col(
      aes(fill = type,
          color = type,
          fill = after_scale(colorspace::darken(fill, .3)),
          color = after_scale(colorspace::darken(color, .3))),
      width = .4,
      size = .1
    ) +
    geom_rect(
      xmin = -Inf, xmax = .8,
      ymin = -Inf, ymax = Inf,
      fill = "white"
    ) +
    geom_text(data = df_polar %>% group_by(type) %>% summarize(pos_cont = unique(pos_cont), sum = unique(sum)),
              aes(1, pos_cont + 50, 
                  label = glue::glue("{type}\npositions")),
              family = "Montserrat",
              fontface = "bold",
              color = "white",
              size = 8,
              lineheight = .9,
              hjust = .5,
              vjust = 0) +
    geom_text(data = df_polar %>% group_by(type) %>% summarize(pos_cont = unique(pos_cont), sum = unique(sum)),
              aes(1, pos_cont, 
                  label = sum),
              family = "Overpass Mono",
              color = "white",
              size = 10,
              lineheight = .9,
              hjust = .5,
              vjust = .5) +
    geom_text(data = df_polar %>% filter(n > 11),
              aes(1.47, pos, 
                  label = word, 
                  color = type,
                  color = after_scale(colorspace::darken(color, .15)),
                  hjust = 0,
                  size = n),
              family = "Montserrat", 
              fontface = "bold") +
    geom_text(data = df_polar %>% filter(n > 11),
              aes(1.33, pos, 
                  label = n, 
                  hjust = .5,
                  size = n / 2),
              family = "Overpass Mono", 
              color = "white") +
    scale_x_continuous(limits = c(0.5, 2.15)) +
    scale_color_manual(values = c(bl_col, "#8800d1"), guide = F) +
    scale_fill_manual(values = c(bl_col, "#8800d1"), guide = F) + 
    scale_alpha(range = c(.3, 1), guide = F) +
    scale_size(range = c(3, 15), guide = F) +
    theme_void()

if(save == T){
  ggsave(here::here("plots", "1_1_jobs_tech.pdf"), width = 12, height = 12, device = cairo_pdf)
}
```

```{r 1-1-popular-job-type-no-specialist, fig.width = 12, fig.height = 10.5}
## technical: analyst, engineer, developer, technician, optimization,
## non-technical: manager, director, writer, consultant, coordinator, editor, marketing, sales, social media 

df_polar <-
  df %>% 
  unnest_tokens(word, job_title, token = "words") %>% 
  anti_join(stop_words) %>% 
  count(word, sort = T) %>% 
  mutate(
    type = case_when(
      str_detect(word, "analy|engine|develop|technic|optimi") ~ "technical",
      str_detect(word, "manage|direct|writ|consult|coordinat|edito|market|sale|social|strateg|supervis") ~ "non-technical",
      TRUE ~ "unknown"
    )
  ) %>%
  filter(type != "unknown") %>% 
  group_by(type) %>% 
  mutate(sum = sum(n)) %>% 
  ungroup %>% 
  arrange(-sum, n) %>% 
  mutate(
    pos = cumsum(n),
    pos = if_else(!is.na(lag(pos)), pos - ((pos - lag(pos)) / 2), pos / 2)
  ) %>% 
  mutate(type = fct_reorder(factor(type), sum)) %>% 
  mutate(country = fct_reorder2(factor(word), as.numeric(type), n, .desc = F)) %>% 
  group_by(type) %>%
  arrange(n) %>% 
  mutate(
    alpha = n / max(n),
    pos_cont = min(pos) + (max(pos) - min(pos)) / 2
  ) 

df_polar %>% 
  ggplot(aes(1, n)) +
    geom_col(
      aes(
        fill = type,
        fill = after_scale(colorspace::darken(fill, .05)), 
        color = type,
        color = after_scale(colorspace::darken(color, .15)), 
        alpha = alpha
      ), 
      size = .1
    ) +
    geom_col(
      aes(fill = type,
          color = type,
          fill = after_scale(colorspace::darken(fill, .3)),
          color = after_scale(colorspace::darken(color, .3))),
      width = .4,
      size = .1
    ) +
    geom_rect(
      xmin = -Inf, xmax = .8,
      ymin = -Inf, ymax = Inf,
      fill = "white"
    ) +
    geom_text(data = df_polar %>% group_by(type) %>% summarize(pos_cont = unique(pos_cont), sum = unique(sum)),
              aes(1, pos_cont + 50, 
                  label = glue::glue("{type}\npositions")),
              family = "Montserrat",
              fontface = "bold",
              color = "white",
              size = 8,
              lineheight = .9,
              hjust = .5,
              vjust = 0) +
    geom_text(data = df_polar %>% group_by(type) %>% summarize(pos_cont = unique(pos_cont), sum = unique(sum)),
              aes(1, pos_cont, 
                  label = sum),
              family = "Overpass Mono",
              color = "white",
              size = 10,
              lineheight = .9,
              hjust = .5,
              vjust = .5) +
    geom_text(data = df_polar %>% filter(n > 11),
              aes(1.47, pos, 
                  label = word, 
                  color = type,
                  color = after_scale(colorspace::darken(color, .15)),
                  hjust = 0,
                  size = n),
              family = "Montserrat", 
              fontface = "bold") +
    geom_text(data = df_polar %>% filter(n > 11),
              aes(1.33, pos, 
                  label = n, 
                  hjust = .5,
                  size = n / 2),
              family = "Overpass Mono", 
              color = "white") +
    scale_x_continuous(limits = c(0.5, 2.15)) +
    scale_color_manual(values = c(bl_col, "#8800d1"), guide = F) +
    scale_fill_manual(values = c(bl_col, "#8800d1"), guide = F) + 
    scale_alpha(range = c(.3, 1), guide = F) +
    scale_size(range = c(3, 15), guide = F) +
    theme_void()


if(save == T){
  ggsave(here::here("plots", "1_1_jobs_tech_no_spec.pdf"), width = 12, height = 10.5, device = cairo_pdf)
}
```


# Convert PDFs to PNGs

```{r convert-pdf-to-png, echo = F}
pdfs <- list.files(here::here("plots"), pattern = "*.pdf")

setwd(here::here("plots", "png"))

for(pdf in pdfs) {
  pdf_convert(pdf = here::here("plots", pdf), 
              format = "png", dpi = 750)
}
```
