---
title: "SEO Jobs Analysis"
author: "Cédric Scherer & Daniel Kupka (FrontPage Data) & Brian Dean (backlinko.com)"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: console
---

<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.showtext = TRUE)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})
```

```{r prep}
## packages
library(tidyverse)
library(tidytext)
library(sf)
library(maps)
library(rgeocodio)
library(geojsonio)
library(rgeos)
library(patchwork)
library(pdftools)
library(showtext)

## save plots?
save <- TRUE
#save <- FALSE

## quality of png's
dpi <- 750

## font
font_add_google("Montserrat", "Montserrat")
font_add_google("Overpass Mono", "Overpass Mono")

## theme updates
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "Montserrat"))

theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 16,
                                       face = "bold",
                                       lineheight = 1.15,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             #plot.title.position = "plot",
             plot.caption = element_text(color = "grey40", 
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))

## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))

## theme settings for maps
theme_map <- 
  theme_void(base_family = "Montserrat") +
  theme(legend.direction = "horizontal",
        legend.box = "horizontal",
        legend.margin = margin(10, 10, 10, 10),
        legend.title = element_text(size = 17, 
                                    face = "bold"),
        legend.text = element_text(color = "grey33",
                                   size = 12),
        plot.margin = margin(15, 5, 15, 5),
        plot.title = element_text(face = "bold",
                                  size = 20,
                                  hjust = .5,
                                  margin = margin(30, 0, 10, 0)),
        plot.subtitle = element_text(face = "bold",
                                     color = "grey33",
                                     size = 17,
                                     hjust = .5,
                                     margin = margin(10, 0, -30, 0)),
        plot.caption = element_text(size = 14,
                                    color = "grey33",
                                    hjust = .97,
                                    margin = margin(-30, 0, 0, 0)))

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)

## main color backlinko
bl_col <- "#00d188"

## colors + labels for interval stripes
int_cols <- c("#bce2d5", "#79d8b6", bl_col, "#009f66", "#006c45", "#003925")
int_perc <- c("100%", "95%", "75%", "50%", "25%", "5%")

## colors for degrees (Bachelors, Massters, Doctorate in reverse order)
cols_degree <- c("#e64500", "#FFCC00", colorspace::darken(bl_col, .1))

## gradient colors for position
colfunc <- colorRampPalette(c(bl_col, "#bce2d5"))
pos_cols <- colfunc(10)
```

```{r data}
df <- readr::read_csv(here::here("raw_data", "Glassdoor - 2020-04-01-0.csv")) %>% 
  janitor::clean_names() %>% 
  dplyr::select(-url)
```


# 1. Job Title

## 1.1 Most Popular SEO Jobs

We analysed the data on job titles using text mining techniques. In a first step, we tokenize the job titles into single words and visualize their frequency. Stop words and words that appeared less than 7 times were removed to make the graph easier to grasp.

```{r 1-1-popular-job-words, fig.width = 12, fig.height = 9}
df %>% 
  unnest_tokens(word, job_title, token = "words") %>% 
  anti_join(stop_words) %>% 
  count(word, sort = T) %>% 
  filter(
    n > 7,
    word != "seo"
  ) %>% 
  mutate(word = if_else(word %in% c("sr", "ppc"), 
                        str_to_upper(word), 
                        str_to_title(word))) %>% 
  ggplot(aes(fct_reorder(word, n), n)) +
    geom_col(fill = bl_col, width = .8) +
    geom_text(aes(label = n),
              family = "Overpass Mono",
              color = "white",
              face = "bold",
              hjust = 1,
              nudge_y = -1) +
    coord_flip() +
    scale_y_continuous(expand = c(.01, .01)) +
    labs(x = NULL, 
         y = "Term frequence in job titles",
         caption = 'Note: Only words with a frequency of 8 or more shown. The term "SEO" was removed.') +
    theme_flip

if(save == T){
  ggsave(here::here("plots", "1_1_jobs_word.pdf"), width = 12, height = 9, device = cairo_pdf)
}
```


In a second step, we analysed sequences of words in the job title. The sorted bar plot shows the most popular consecutive sequences of words (5 or more occurences), colored by category.

```{r 1-1-popular-jobs-ngrams-cat, fig.width = 12, fig.height = 7.5}
df_job_ngrams <-
  df %>% 
  unnest_tokens(word, job_title, token = "ngrams") %>% 
  anti_join(stop_words) %>% 
  count(word, sort = T) %>% 
  filter(
    n > 4,
    !is.na(word)
  ) %>% 
  mutate(
    group = case_when(
      str_detect(word, "content") ~ "Content",
      str_detect(word, "manager") ~ "Management",
      str_detect(word, "analyst") ~ "Analysis",
      str_detect(word, "strategist") ~ "Strategy",
      str_detect(word, "optimiz") ~ "Optimization",
      str_detect(word, "market") ~ "Marketing",
      str_detect(word, "specialist") ~ "Analysis",
      TRUE ~ "Other"
    ),
    word = str_to_title(word)
  ) 
  
ggplot(df_job_ngrams, 
       aes(fct_reorder(word, n), n)) +
    geom_col(aes(fill = group), 
             width = .8) +
    geom_text(aes(label = n),
              family = "Overpass Mono",
              color = "white",
              face = "bold",
              hjust = 1,
              nudge_y = -.7) +
    coord_flip() +
    scale_y_continuous(expand = c(.01, .01)) +
    scale_fill_manual(name = "Job Category",
                      values = c("#2d6db4", "#633b96", "#e49e2e", "#b8318c", "#00b877", "#96633b")) +
    guides(fill = guide_legend(ncol = 1)) +
    labs(x = NULL, 
         y = "Frequence of word sequence in job titles",
         caption = "Note: Only sequences with a frequency of 5 or more shown.") +
    theme_flip +
    theme(legend.position = c(.68, .627),
          legend.key.size = unit(3, "pt"),
          legend.key.width = unit(30, "pt"))

if(save == T){
  ggsave(here::here("plots", "1_1_jobs_cat.pdf"), width = 12, height = 7.5, device = cairo_pdf)
}
```


We  manually classified in technical and non-technical positions, removing all words that are no specific to any of the both categories. This modified stacked bar plot shows the number of words found per job category and, additionally as another stacked bar next to it, the most common words per category (with labels for words that occured at least 20 times). The height of the stacks indicates as well the number, the width is arbitrary.

```{r 1-1-popular-job-type, fig.width = 12, fig.height = 12}
## technical: analyst, specialist, engineer, developer, technician, optimization,
## non-technical: manager, director, writer, consultant, coordinator, editor, marketing, sales, social media 

df_polar <-
  df %>% 
  unnest_tokens(word, job_title, token = "words") %>% 
  anti_join(stop_words) %>% 
  count(word, sort = T) %>% 
  mutate(
    type = case_when(
      str_detect(word, "analy|special|engine|develop|technic|optimi") ~ "technical",
      str_detect(word, "manage|direct|writ|consult|coordinat|edito|market|sale|social|strateg|supervis") ~ "non-technical",
      TRUE ~ "unknown"
    )
  ) %>%
  filter(type != "unknown") %>% 
  group_by(type) %>% 
  mutate(sum = sum(n)) %>% 
  ungroup %>% 
  arrange(sum, n) %>% 
  mutate(
    pos = cumsum(n),
    pos = if_else(!is.na(lag(pos)), pos - ((pos - lag(pos)) / 2), pos / 2)
  ) %>% 
  mutate(type = fct_reorder(factor(type), -sum)) %>% 
  mutate(country = fct_reorder2(factor(word), as.numeric(type), n, .desc = F)) %>% 
  group_by(type) %>%
  arrange(n) %>% 
  mutate(
    alpha = n / max(n),
    pos_cont = min(pos) + (max(pos) - min(pos)) / 2
  ) 

df_polar %>% 
  ggplot(aes(1, n)) +
    geom_col(
      aes(
        fill = type,
        fill = after_scale(colorspace::darken(fill, .05)), 
        color = type,
        color = after_scale(colorspace::darken(color, .15)), 
        alpha = alpha
      ), 
      size = .1
    ) +
    geom_col(
      aes(fill = type,
          color = type,
          fill = after_scale(colorspace::darken(fill, .3)),
          color = after_scale(colorspace::darken(color, .3))),
      width = .4,
      size = .1
    ) +
    geom_rect(
      xmin = -Inf, xmax = .8,
      ymin = -Inf, ymax = Inf,
      fill = "white"
    ) +
    geom_text(data = df_polar %>% group_by(type) %>% summarize(pos_cont = unique(pos_cont), sum = unique(sum)),
              aes(1, pos_cont + 50, 
                  label = glue::glue("{type}\ntitle terms")),
              family = "Montserrat",
              fontface = "bold",
              color = "white",
              size = 8,
              lineheight = .9,
              hjust = .5,
              vjust = 0) +
    geom_text(data = df_polar %>% group_by(type) %>% summarize(pos_cont = unique(pos_cont), sum = unique(sum)),
              aes(1, pos_cont, 
                  label = sum),
              family = "Overpass Mono",
              color = "white",
              size = 10,
              lineheight = .9,
              hjust = .5,
              vjust = .5) +
    geom_text(data = df_polar %>% filter(n > 11),
              aes(1.47, pos, 
                  label = word, 
                  color = type,
                  color = after_scale(colorspace::darken(color, .15)),
                  hjust = 0,
                  size = n),
              family = "Montserrat", 
              fontface = "bold") +
    geom_text(data = df_polar %>% filter(n > 11),
              aes(1.33, pos, 
                  label = n, 
                  hjust = .5,
                  size = n / 2),
              family = "Overpass Mono", 
              color = "white") +
    scale_x_continuous(limits = c(0.5, 2.15)) +
    scale_color_manual(values = c(bl_col, "#8800d1"), guide = F) +
    scale_fill_manual(values = c(bl_col, "#8800d1"), guide = F) + 
    scale_alpha(range = c(.3, 1), guide = F) +
    scale_size(range = c(3, 15), guide = F) +
    theme_void()

if(save == T){
  ggsave(here::here("plots", "1_1_jobs_tech.pdf"), width = 12, height = 12, device = cairo_pdf)
}
```

```{r 1-1-popular-job-type-no-specialist, fig.width = 12, fig.height = 10.5}
## technical: analyst, engineer, developer, technician, optimization,
## non-technical: manager, director, writer, consultant, coordinator, editor, marketing, sales, social media 

df_polar <-
  df %>% 
  unnest_tokens(word, job_title, token = "words") %>% 
  anti_join(stop_words) %>% 
  count(word, sort = T) %>% 
  mutate(
    type = case_when(
      str_detect(word, "analy|develop|technic|data") ~ "technical",
      str_detect(word, "manage|direct|writ|consult|coordinat|edito|market|sale|social|strateg|supervis") ~ "non-technical",
      TRUE ~ "unknown"
    )
  ) %>%
  filter(type != "unknown") %>% 
  group_by(type) %>% 
  mutate(sum = sum(n)) %>% 
  ungroup %>% 
  arrange(-sum, n) %>% 
  mutate(
    pos = cumsum(n),
    pos = if_else(!is.na(lag(pos)), pos - ((pos - lag(pos)) / 2), pos / 2)
  ) %>% 
  mutate(type = fct_reorder(factor(type), sum)) %>% 
  mutate(country = fct_reorder2(factor(word), as.numeric(type), n, .desc = F)) %>% 
  group_by(type) %>%
  arrange(n) %>% 
  mutate(
    alpha = n / max(n),
    pos_cont = min(pos) + (max(pos) - min(pos)) / 2
  ) 

df_polar %>% 
  ggplot(aes(1, n)) +
    geom_col(
      aes(
        fill = type,
        fill = after_scale(colorspace::darken(fill, .05)), 
        color = type,
        color = after_scale(colorspace::darken(color, .15)), 
        alpha = alpha
      ), 
      size = .1
    ) +
    geom_col(
      aes(fill = type,
          color = type,
          fill = after_scale(colorspace::darken(fill, .3)),
          color = after_scale(colorspace::darken(color, .3))),
      width = .4,
      size = .1
    ) +
    geom_rect(
      xmin = -Inf, xmax = .8,
      ymin = -Inf, ymax = Inf,
      fill = "white"
    ) +
    geom_text(data = df_polar %>% group_by(type) %>% summarize(pos_cont = unique(pos_cont), sum = unique(sum)),
              aes(1, pos_cont + 35, 
                  label = glue::glue("{type}\ntitle terms")),
              family = "Montserrat",
              fontface = "bold",
              color = "white",
              size = 8,
              lineheight = .9,
              hjust = .5,
              vjust = 0) +
    geom_text(data = df_polar %>% group_by(type) %>% summarize(pos_cont = unique(pos_cont), sum = unique(sum)),
              aes(1, pos_cont, 
                  label = sum),
              family = "Overpass Mono",
              color = "white",
              size = 10,
              lineheight = .9,
              hjust = .5,
              vjust = .5) +
    geom_text(data = df_polar %>% filter(n >= 5),
              aes(1.47, pos, 
                  label = word, 
                  color = type,
                  color = after_scale(colorspace::darken(color, .15)),
                  hjust = 0,
                  size = n),
              family = "Montserrat", 
              fontface = "bold") +
    geom_text(data = df_polar %>% filter(n >= 20),
              aes(1.33, pos, 
                  label = n, 
                  hjust = .5,
                  size = n / 2),
              family = "Overpass Mono", 
              color = "white") +
    scale_x_continuous(limits = c(0.5, 2.15)) +
    scale_color_manual(values = c(bl_col, "#8800d1"), guide = F) +
    scale_fill_manual(values = c(bl_col, "#8800d1"), guide = F) + 
    scale_alpha(range = c(.3, 1), guide = F) +
    scale_size(range = c(2, 15), guide = F) +
    theme_void()


if(save == T){
  ggsave(here::here("plots", "1_1_jobs_tech_adj.pdf"), width = 12, height = 14.5, device = cairo_pdf)
}
```




# 2. Location

* Where do companies hire SEOs? (beautiful US Map)

```{r map-prep}
## usa map
states <- 
  st_as_sf(map("state", plot = F, fill = T)) %>% 
  st_transform(2163)

df_loc <-
  df %>% 
  group_by(location) %>% 
  count(sort = T) %>% 
  ungroup()
```

## 2.1 Hot Spots (Cities)

```{r 2-1-map-cities, fig.width = 15, fig.height = 9.7}
## add geocodes of cities
path <- here::here("proc_data", "geocodes.Rds")

if(file.exists(path)){
  ## load geocodes or...
  df_geo <- readRDS(path)
}else{
  ## grab and save geocodes
  df_geo <- 
    gio_batch_geocode(df_loc$location) %>% 
    unnest(response_results, .preserve = response_warnings) %>% 
    dplyr::select(query, formatted_address, location.lat, location.lng) %>% 
    group_by(query) %>% 
    slice(1)
  
  saveRDS(df_geo, path)
}

sf_map <-
  df_loc %>% 
  left_join(df_geo, by = c("location" = "query")) %>% 
  filter(!is.na(location.lng)) %>% 
  st_as_sf(coords = c("location.lng", "location.lat"), 
           crs = 4326) %>% 
  st_transform(st_crs(states)) %>% 
  st_crop(st_bbox(states))
  
sf_map %>% 
  arrange(-n) %>% 
  ggplot() +
    geom_sf(data = states, 
            #color = colorspace::darken(bl_col, .05), 
            color = "grey60",
            alpha = .3,
            lwd = 5) +
    geom_sf(data = states, 
            color = "white", 
            fill = "#cedbd7",
            lwd = .5) +
    geom_sf(aes(size = n),
            color = "white",
            show.legend = "point") +
    geom_sf(aes(size = n), 
            shape = 21, 
            color = colorspace::darken(bl_col, .2),
            fill = NA,
            stroke = .4,
            show.legend = "point") +
    geom_sf(aes(size = n, color = n), 
            color = bl_col,
            alpha = .1,
            show.legend = "point") +
    scale_size(range = c(3, 30), 
               breaks = c(1, 10, 25, 50, 100),
               name = "Number of job offers") +
    guides(size = guide_legend(title.position = "top", 
                                title.hjust = .5, 
                                nrow = 1,
                                label.position = "bottom",
                                override.aes = list(shape = 21, color = bl_col, fill = colorspace::lighten(bl_col, .9), stroke = 1))) +
    theme_map +
    theme(legend.position = c(.2, .1),
          legend.title = element_text(margin = margin(0, 0, -5, 0)),
          legend.text = element_text(margin = margin(-10, 0, 0, 0)))

if(save == T){ 
  ggsave(here::here("plots", "2_1_map_cities.pdf"), 
         width = 15, height = 9.7, device = cairo_pdf) 
}
```


## 2.2 Hot Spots (States)

```{r map-states-hex-prep}
## data by states
df_states <-
  readr::read_csv(here::here("raw_data", "50_us_states_all_data.csv"), 
                  col_names = F) %>% 
  dplyr::select(state = "X2", ISO2 = "X3")%>% 
  add_row(state = "District of Colombia", ISO2 = "DC")

df_states_join <-
  df_loc %>% 
  mutate(location = str_replace(location, ", United States|, US", "")) %>% 
  mutate(state_mixed = str_extract(location, "[^, ]*$")) %>% 
  left_join(df_states, by = c("state_mixed" = "ISO2")) %>%
  mutate(state = if_else(is.na(state), state_mixed, state)) %>% 
  group_by(state) %>% 
  count(sort = T) %>% 
  ungroup()

## hex map
map_hex <- geojson_read(here::here("raw_data", "us_states_hexgrid.geojson.json"),  what = "sp")

map_hex@data <-
  map_hex@data %>%
  mutate(google_name = gsub(" \\(United States\\)", "", google_name))

map_hex_fortified <- tidy(map_hex, region = "google_name")

## combine data
df_hex <- 
  map_hex_fortified %>%
  left_join(df_states_join, by = c("id" = "state"))

## centroids for labels
centroids <- cbind.data.frame(data.frame(gCentroid(map_hex, byid = T), 
                                         id = map_hex@data$iso3166_2,
                                         id_long = str_wrap(map_hex@data$google_name, 12))) %>% 
  left_join(df_hex, by = c("id_long" = "id")) %>% 
  group_by(id) %>% 
  slice(1) %>% 
  replace_na(list(n = 0))
```


```{r 2-2-map-states-hex, fig.width = 15, fig.height = 9.7}
df_hex %>%
  replace_na(list(n = 0)) %>% 
  ggplot() +
    geom_polygon(aes(long, lat, 
                     group = group, 
                     fill = n), 
                 #color = colorspace::darken(bl_col, .1),
                 color = "grey60",
                 lwd = .8) +
    geom_text(data = centroids, 
              aes(x = x, y = y + 0.35,
                  label = n,
                  alpha = n),
              family = "Montserrat",
              fontface = "bold",
              size = 7.5,
              color = colorspace::darken(bl_col, .6),
              vjust = .2) +
    geom_text(data = centroids, 
              aes(x = x, y = y - 0.3, label = id_long),
              family = "Montserrat",
              fontface = "bold",
              size = 3.2,
              lineheight = 0.85,
              vjust = 1) +
    coord_map() + 
    scale_fill_gradient(low = "grey95", 
                        high = colorspace::darken(bl_col, .1), 
                        name = "Number of job offers",
                        limits = c(0, 50),
                        breaks = seq(0, 50, by = 5)) +
    scale_alpha(range = c(.25, 1), 
                guide = F) +
    guides(fill = guide_colorbar(barheight = unit(5, units = "mm"),  
                                 barwidth = unit(150, units = "mm"),
                                 direction = "horizontal",
                                 ticks.colour = "#e8d8c3",
                                 title.position = "top",
                                 title.hjust = 0.5)) +
    theme_map +
    theme(legend.position = c(.5, .9),
          legend.text = element_text(size = 14))

if(save == T){ 
  ggsave(here::here("plots", "2_2_map_hex_states.pdf"), 
         width = 15, height = 9.7, device = cairo_pdf) 
}
```



# 3. Company Info

## 3.1	Size

```{r data-prep-size}
df_size <- 
  df %>% 
  dplyr::select(size, description) %>% 
  mutate(
    size = if_else(is.na(size), "Unknown", size),
    size = str_replace(size, " employees", ""),
    size = str_replace(size, " to ", "–"),
    size = factor(size, 
                  levels = c("1–50", "51–200", "201–500", "501–1000", 
                             "1001–5000", "5001–10000", "10000+", "Unknown"),
                  labels = c("1–50", "51–200", "201–500", "501–1,000", 
                             "1,001–5,000", "5,001–10,000", "10,000+", "Unknown"),
                  )
  )
```


* How large are companies that hire? 

```{r 3-1-size-histogram-size, fig.width = 12, fig.height = 8}
df_size %>% 
  group_by(size) %>% 
  count() %>%
  mutate(col = if_else(size == "Unknown", "A", "B")) %>% 
  ggplot(aes(size, n)) +
    geom_col(aes(fill = col, 
                 color = after_scale(colorspace::darken(fill, .4))),
             width = .85,
             size = 1) +
    scale_y_continuous(expand = c(.0075, .0075)) +
    scale_fill_manual(values = c("grey60", bl_col),
                      guide = F) +
    labs(x = "Number of Employees", 
         y = "Number of companies") +
    theme(panel.grid.major.x = element_blank())

if(save == T){ 
  ggsave(here::here("plots", "3_1_size_histo.pdf"), 
         width = 12, height = 8, device = cairo_pdf) 
}
```


* Do larger companies require more specialized tasks? 

--> What do we define as "more specialized tasks"?


* Do larger companies require a formal education?

```{r 3-1-size-education, fig.width = 12, fig.height = 7.5}
df_size_edu <-
  df_size %>% 
  mutate(
    bachelors = if_else(str_detect(description, "B.Ba.|B.Sc.|BBa|BSc|BBA|BSC|Bachelors"), 1, 0),
    masters = if_else(str_detect(description, "M.Ba.|M.Sc.|MBa|MSc|MBA|MSC|Masters"), 1, 0),
    doctorate = if_else(str_detect(description, "Ph.D.|PhD|Doctorate"), 1, 0)
  ) %>% 
  dplyr::select(size, bachelors, masters, doctorate) %>% 
  pivot_longer(
    cols = c(bachelors, masters, doctorate),
    names_to = "education",
    values_to = "yes_no"
  ) %>%
  group_by(size) %>% 
  mutate(
    total = n(),
    education = str_to_title(education),
    education = factor(education, levels = c("Doctorate", "Masters", "Bachelors"))
  ) %>% 
  group_by(size, education) %>% 
  summarize(rel = sum(yes_no) / unique(total)) %>% 
  ungroup()

ggplot(df_size_edu, 
       aes(size, rel, 
           fill = education)) +
  geom_col(width = .8) +
  scale_y_continuous(expand = c(.0005, .0005),
                     limits = c(0, .031),
                     labels = scales::percent_format()) +
  scale_fill_manual(values = cols_degree, 
                    name = "Required degree:") +
  guides(fill = guide_legend(reverse = T)) +
  theme(legend.text = element_text(size = 14),
        panel.grid.major.x = element_blank()) +
  labs(x = "Number of employees", 
       y = "Percentage")

if(save == T){ 
  ggsave(here::here("plots", "3_1_size_edu.pdf"), 
         width = 12, height = 7.5, device = cairo_pdf) 
}
```

Bachelors: 38
Masters: 10
Doctorate: 1

## 3.2	Revenue

```{r data-prep-revenue}
df_revenue <-
  df %>% 
  dplyr::select(revenue, description) %>% 
  mutate(
    revenue = if_else(revenue == "Unknown / Non-Applicable", "Unknown", revenue),
    revenue = if_else(is.na(revenue), "Unknown", revenue),
    revenue = str_replace(revenue, " \\(USD\\)", ""),
    revenue = str_replace(revenue, " million", "M"),
    revenue = str_replace(revenue, " billion", "B"),
    revenue = str_replace(revenue, " to \\$", "–"),
    revenue = str_replace(revenue, "Less than", "<"),
    revenue = if_else(revenue == "$10+B", "> $10B", revenue),
    revenue = factor(revenue,
                     levels = c("< $1M", "$1–5M", "$5–10M", "$10–25M",
                                "$25–50M", "$50–100M", "$100–500M", "$500M–1B",
                                "$1–2B", "$2–5B", "$5–10B", "> $10B",
                                "Unknown"))
  )
```


* Which education level is required by high-revenue companies?

```{r 3-2-revenue-education, fig.width = 12, fig.height = 7.5}
df_rev_edu <-
  df_revenue %>% 
  mutate(
    bachelors = if_else(str_detect(description, "B.Ba.|B.Sc.|BBa|BSc|BBA|BSC|Bachelors"), 1, 0),
    masters = if_else(str_detect(description, "M.Ba.|M.Sc.|MBa|MSc|MBA|MSC|Masters"), 1, 0),
    doctorate = if_else(str_detect(description, "Ph.D.|PhD|Doctorate"), 1, 0)
  ) %>% 
  dplyr::select(revenue, bachelors, masters, doctorate) %>% 
  pivot_longer(
    cols = c(bachelors, masters, doctorate),
    names_to = "education",
    values_to = "yes_no"
  ) %>%
  group_by(revenue) %>% 
  mutate(
    total = n(),
    education = str_to_title(education),
    education = factor(education, levels = c("Doctorate", "Masters", "Bachelors"))
  ) %>% 
  group_by(revenue, education) %>% 
  summarize(rel = sum(yes_no) / unique(total)) %>% 
  ungroup()

ggplot(df_rev_edu, aes(revenue, rel, 
                   fill = education)) +
  geom_col(width = .8) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(expand = c(.0005, .0005),
                     limits = c(0, .031),
                     labels = scales::percent_format()) +
  scale_fill_manual(values = cols_degree, 
                    name = "Required degree:") +
  guides(fill = guide_legend(reverse = T)) +
  theme(legend.text = element_text(size = 14),
        panel.grid.major.x = element_blank()) +
  labs(x = "Estimated revenue", 
       y = "Percentage")

if(save == T){ 
  ggsave(here::here("plots", "3_2_revenue_edu_dodge.pdf"), 
         width = 12, height = 6.5, device = cairo_pdf) 
}

ggplot(df_rev_edu, aes(revenue, rel, 
                   fill = education)) +
  geom_col(width = .8) +
  scale_y_continuous(expand = c(.0005, .0005),
                     limits = c(0, .031),
                     labels = scales::percent_format()) +
  scale_fill_manual(values = cols, 
                    name = "Required degree:") +
  guides(fill = guide_legend(reverse = T)) +
  theme(legend.text = element_text(size = 14),
        panel.grid.major.x = element_blank(),
        axis.text.x = element_text(size = 9)) +
  labs(x = "Estimated revenue", 
       y = "Percentage")

if(save == T){ 
  ggsave(here::here("plots", "3_2_revenue_edu_small.pdf"), 
         width = 12, height = 6.5, device = cairo_pdf) 
}

ggplot(df_rev_edu, aes(revenue, rel, 
                   fill = education)) +
  geom_col(width = .8) +
  scale_y_continuous(expand = c(.0005, .0005),
                     limits = c(0, .031),
                     labels = scales::percent_format()) +
  scale_fill_manual(values = cols_degree, 
                    name = "Required degree:") +
  guides(fill = guide_legend(reverse = T)) +
  theme(legend.text = element_text(size = 14),
        panel.grid.major.x = element_blank(),
        axis.text.x = element_text(angle = 22, hjust = 1, vjust = 1)) +
  labs(x = "Estimated revenue", 
       y = "Percentage")

if(save == T){ 
  ggsave(here::here("plots", "3_2_revenue_edu_angle.pdf"), 
         width = 12, height = 6.5, device = cairo_pdf) 
}
```

* What type of skill sets are required by high-revenue companies?

-> Can you come up with a list or should I try to extract common words? DOn't know yet how to determine those terms between skills and... yeah, what does mark the end of the skill section?

-> So I tokenized the description and removed stop words and numbers as well as manually non-sense/non-skill-related words. There might be more but if we keep it we can have a closer look I would say.

```{r 3-2-revenue-skills, fig.width = 12, fig.height = 7.5}
df_rev_skills <-   
  df_revenue %>% 
  unnest_tokens(word, description, token = "words") %>% 
  anti_join(stop_words) %>% 
  filter(
    !word %in% c("seo","experience", "skills", "skill", "ability", "requirement", "requirements", "link", "required", "provide", "day", "email", "based", "growth", "recommendations", "employment", "paid", "payment", "key", "gender", "equal", "applicants", "application", "disability", "disabilities", "world", "qualifications", "multiple", "page", "pages", "related", "site", "candidate", "insurance", "company", "agency", "office", "position"),
    !str_detect(word, "[0-9+]")
  ) %>% 
  mutate(word = if_else(word == "teams", "team", word))

set.seed(2020)

cloud_low <-
  df_rev_skills %>% 
  filter(revenue %in% c("< $1M", "$1–5M", "$5–10M", "$10–25M",
                        "$25–50M", "$50–100M")) %>% 
  count(word, sort = T) %>% 
  top_n(75, n) %>% 
  ggplot(aes(label = word, size = n, color = n)) +
    geom_text_wordcloud(
      family = "Montserrat",
      fontface = "bold",
      shape = "square"
    ) +
    rcartocolor::scale_color_carto_c(palette = "Emrld") +
    scale_size_area(max_size = 9) +
    labs(title = "\nCompanies with revenues lower than $100M") +
    theme_minimal()

cloud_high <-
  df_rev_skills %>% 
  filter(revenue %in% c("$100–500M", "$500M–1B",
                        "$1–2B", "$2–5B", "$5–10B", "> $10B")) %>% 
  count(word, sort = T) %>% 
  top_n(75, n) %>% 
  ggplot(aes(label = word, size = n, color = n)) +
    geom_text_wordcloud(
      family = "Montserrat",
      fontface = "bold",
      shape = "square"
    ) +
    rcartocolor::scale_color_carto_c(palette = "Emrld") +
    scale_size_area(max_size = 9) +
    labs(title = "\nCompanies with revenues higher than $100M") +
    theme_minimal()

## vertical allignment
(cloud_low / cloud_high) * 
  theme(plot.title = element_text(family = "Montserrat", size = 14, face = "bold", 
                                  hjust = .5, margin = margin(b = 15)))

if(save == T){ 
  ggsave(here::here("plots", "3_2_revenue_words_vertical.pdf"), 
         width = 10, height = 7, device = cairo_pdf) 
}


## horizontal allignment
(cloud_low + cloud_high) * 
  theme(plot.title = element_text(family = "Montserrat", size = 14, face = "bold", 
                                  hjust = .5, margin = margin(b = -15)))

if(save == T){ 
  ggsave(here::here("plots", "3_2_revenue_words_horizontal.pdf"), 
         width = 16, height = 5.1, device = cairo_pdf) 
}
```


## 3.3	Sector/Industry

* What type of companies hire SEOs? 

```{r 3-3-sector}
df %>% 
  filter(!is.na(sector)) %>% 
  group_by(sector) %>% 
  count(sort = T) %>% 
  ungroup() %>% 
  mutate(sector = fct_reorder(factor(sector), n)) %>% 
  ggplot(aes(sector, n)) +
    geom_col(width = .8, fill = bl_col) +
    geom_text(aes(label = n),
              family = "Overpass Mono",
              color = "grey40",
              fontface = "bold",
              hjust = 0,
              nudge_y = 3,
              size = 2.5) +
    coord_flip() +
    scale_y_continuous(expand = c(.01, .01),
                       limits = c(0, 345),
                       breaks = seq(0, 300, by = 50)) +
    labs(x = NULL, y = "Number of job offers by sector") +
    theme_flip

if(save == T){ 
  ggsave(here::here("plots", "3_3_sector_counts.pdf"), 
         width = 12, height = 6.5, device = cairo_pdf) 
}
```

```{r 3-3-industry}
df %>% 
  filter(!is.na(industry)) %>% 
  group_by(industry) %>% 
  count(sort = T) %>% 
  filter(n > 4) %>% 
  ungroup() %>% 
  mutate(industry = fct_reorder(factor(industry), n)) %>% 
  ggplot(aes(industry, n)) +
    geom_col(width = .8, fill = bl_col) +
    geom_text(aes(label = n),
              family = "Overpass Mono",
              color = "grey40",
              fontface = "bold",
              hjust = 0,
              nudge_y = 3,
              size = 2.5) +
    coord_flip() +
    scale_y_continuous(expand = c(.01, .01),
                       limits = c(0, 265),
                       breaks = seq(0, 250, by = 50)) +
    labs(x = NULL, y = "Number of job offers by industry",
         caption = "Note: Only industries with 5 or more job offers shown.") +
    theme_flip

if(save == T){ 
  ggsave(here::here("plots", "3_3_industry_counts.pdf"), 
         width = 12, height = 6.5, device = cairo_pdf) 
}
```


## 3.4	Company Rating

* Do lower rated companies pay less (salary)? Which companies have the highest ratings? 

```{r 3-4-rating-salary}
df %>% 
  dplyr::select(salary, ratings) %>% 
  filter(
    !is.na(salary),
    !is.na(ratings)
  ) %>% 
  mutate(
    salary_low = str_extract(salary, "\\$.*\\-"),
    salary_high = str_extract(salary, "\\-\\$.*"),
  ) %>% 
  mutate_at(vars(matches("salary_")), ~str_extract(., "[0-9]+")) %>% 
  mutate_at(vars(matches("salary_")), as.numeric) %>% 
  mutate(salary_avg = salary_low + salary_high / 2) %>% 
  ggplot(aes(ratings, salary_avg)) + 
    geom_smooth(color = colorspace::darken(bl_col, .2), 
                se = F) +
    geom_point(shape = 1,
               size = 4, 
               color = bl_col,
               stroke = .2) +
    geom_point(size = 4, 
               alpha = .1, 
               color = bl_col) +
    scale_y_continuous(breaks = seq(50, 300, by = 50),
                       limits = c(50, 300)) +
    labs(x = "Company rating", 
         y = "Average salary (calculated from range)")

if(save == T){ 
  ggsave(here::here("plots", "3_4_rating_salary.pdf"), 
         width = 12, height = 7.5, device = cairo_pdf) 
}
```


# 4	Job Responsibilities

## 4.1	Job related tasks

* What job tasks are most often mentioned? 


## 4.2	Deep dive into job tasks (PPC, content management, technical, etc.)

* What technical SEO tasks are most often required?


# 5	Job Requirements

## 5.1	Programming Languages

* What programming languages are most often required? 

* What languages are most often required in combination (e.g. Html, CSS)


## 5.2	Knowledge of Popular Tools

* What tools are most often required?


## 5.3	Years of Experience

* What type of SEO jobs require +5 years experience? 


## 5.4	Degree Requirements

* What type of degrees are most often required (BS vs MS vs None)? 


# 6	Salaries

## 6.1	Salary Ranges

* What are the typcial salary ranges for SEO jobs?


## 6.2	Salaries per Location

* Where do companies pay the most/least?


## 6.3	Salaries for different positions

* What are the highest/lowest paying SEO positions?


## 6.4	Salaries per job requirements

* Do positions with programming languages pay significantly more?






# Convert PDFs to PNGs

```{r convert-pdf-to-png, echo = F}
pdfs <- list.files(here::here("plots"), pattern = "*.pdf")

setwd(here::here("plots", "png"))

for(pdf in pdfs) {
  pdf_convert(pdf = here::here("plots", pdf), 
              format = "png", dpi = 750)
}
```
